### 2018-11-13 Sections/essays_quantum_ecosystem.tex
QEC

In the quantum era we anticipate the same phenomena to arise. What will this quantum ecosystem look like?

@@

\item Quantum memory:\index{Quantum memory} Storing qubits with long decoherence lifetimes is extremely challenging using today's technology, and it is foreseeable that vendors might specialise in this particular operation, especially once error correction is built into the memory. 
\end{itemize}

>>>>

In the quantum era we anticipate the same phenomena to arise. What will this quantum ecosystem look like? Here are some of the elements that vendors might specialise in, providing compatible components for the quantum ecosystem:

@@

\item Quantum memory:\index{Quantum memory} Storing qubits with long decoherence lifetimes is extremely challenging using today's technology, and it is foreseeable that vendors might specialise in this particular operation, especially once error correction is built into the memory.

\item Quantum error correction:\index{Quantum error correction} Any given quantum error correcting code follows a well-defined recipe for encoding, correction, and decoding. Thus, it might become an example of a subroutine specialised in by a dedicated quantum error correction vendor, and licensed out as building block for embedding into larger, fault-tolerant\index{Fault-tolerance} protocols.
\end{itemize}
